\documentclass{article}

\usepackage{graphicx}
\usepackage{amsmath}

\title{APG4005F Assignment 3 - Free Network Adjustment}
\date{07/05/2015}
\author{Jason David Russell - RSSJAS005}

\begin{document}

\maketitle
\pagenumbering{gobble}

\newpage
\tableofcontents

\pagenumbering{arabic}

\newpage
\section{Introduction}
The aim of this assignment is to conduct an Epoch deformation analysis using
fictitious data with a Free Network least squares adjustment.


\section{Background}
\subsection{Classification of Deformation Analysis}
There are three main classifications of deformation analysis monitoring methods,
Permanent, Semi-permanet and Epoch. There are advantages and disadvantages of all
three methods. The main advantages of the permanent and Semi-permanent methods
are that they are continuous and offer a very high precision. These two methods
make use of a multitude of sensors, such as capacitive, strain, inductance and
electro-optical sensors. These sensors are able to produce data in real time which
is useful for situations in which immediate data is required in order to, for
example, raise an alarm. Some of the disadvantages of these two methods of
deformation analysis is that the senors are expensive, and require regular
calibration. Epoch monitoring involves geodetic and/or photogramerric techniques
to capture data, this is beneficial in that relative and/or absolute positions of
many points can be obtained, as apposed to just relative positions in the case
of the Permanent and Semi-permanent methods mentioned above. Another advantage
of Epoch monitering is that it is much more cost effective.

\subsection{Network Classifications}
Typically, when constructing a network for Epoch deformation anaylis,
a free or minimum constrained network is used, preferably free. In a free
network adjustment, no parameter is held fixed, and as a result, precision
estimates for all points are provided in the variance-covariance matrices.
The effect of holding no parameters fixed is that the shape of the network
is defined only by the observations. One of the main advantages of not holding
any parameters fixed is that the shape of the network is not affected by erros in
the coordinates of the points defining the datum (because the network is not tied
to the datum and is allowed to `float'). Free networks are especially useful
in cases where precise surveys are connected to existing point coordinates
of lower precisions. A caveat of the free network adjustment is that because the
datum is not defined (no points are fixed) a singular normal equation matrix
will occur (a rank defect occurs in the normal equation matrix).
As singular matrices have a determinant of zero (because one of the
eigen values is zero) the normal equation matrix cannot be inversed, and so
a solution vector `x' cannot be obtained. In order to negate the singular normal
equation matrix, special mathematical treatment based on the determination of a
generalized inverse is applied. To remove the singularity in the normal equation
matrix, a set of pseudo-obseravtion equations are added to to the normal
equation matrix in such a way that these equations remove the singularity and
do not affect the result vector `x'.

\subsection{Concepts of deformation analysis using geodetic method}

\subsubsection{Points selection}
Points representing the feature to be monitored are selected.
The placement of deformation control points must adhere to two criteria:
The network configuration must follow the principles of conventional geodetic
network design, and the selected points must be representative of the feature
in question and points should be suitably placed so as to effectively detect and
model any deformation.

\subsubsection{Network}
A network pre-analyisis based on the least squares adjustment theory should be
undertaken. Then, a conventional network of appropriate accuracy should be
executed in at least two epochs. In terms of coordinate system to use, Local
systems are adequate and preferable, as larger scale coordinate systems are
usually of a poorer precision.

\subsubsection{Deformation Models}
One of a variety of available deformation analysis techniques based on statistical
testing is used to detect if point deformations have occurred. Often, a second
method is employed to confirm the first analysis.

\subsubsection{Inspection}
The quantities and directions of deformations are determined.


\section{Problem Statement}

\section{Method}

\section{Results}

\section{Discussion}

\section{Conclusion}

\end{document}
